Forecasting the US Election 2024

### 2024-11-03 paper/paper.qmd
update r package usages

library(tidyverse)
library(gt)
library(ggplot2)
library(tidyr)
# Load the arrow package
library(arrow)
library(here)
data = read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
# Read the Parquet file
analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))

@@

We use the polling data to forecast the potential outcomes of the 2024 U.S. presidential election between Kamala Harris and Donald Trump.The dataset was obtained from https://projects.fivethirtyeight.com/polls/president-general/2024/national/ or (FiveThirtyEight’s “Poll of Polls” for the 2024 U.S. Presidential election [@fivethirtyeight2024]). It provides a comprehensive view of voter preferences through aggregated results from numerous national polls conducted by various polling organizations. The dataset was simulated, cleaned, analyzed, and tested using the R programming language [@talia], tidyverse [@citetidyverse], knitr [@citeknitr], ggplot2 [@citeggplot2], gt[@gt].

@@

```{r}
#| label: fig-reliability
#| fig-cap: "Average Support Percentage by Pollster Reliability"
#| echo: false
library(ggplot2)

@@

library(tidyverse)
library(gt)

@@

```{r}
#| label: fig-samplesize
#| fig-cap: "Candidate Vote Percentages by Sample Size Category"
#| echo: false
# Categorizing sample size into small, medium, and large groups
library(tidyverse)
library(ggplot2)

@@

```{r}
#| label: fig-sponsorship
#| fig-cap: "Vote Percentages by Partisan Sponsorship"
#| echo: false
# Calculate the average pct and standard deviation for each candidate by sponsorship type
sponsorship_summary_data <- data %>%
  filter(sponsor_candidate_party != "Non-Partisan") %>%  # Focus on partisan-sponsored polls
  group_by(candidate_name, sponsor_candidate_party) %>%
  summarise(
    avg_pct = mean(pct),
    sd_pct = sd(pct),
    .groups = 'drop'
  )
library(ggplot2)

@@

library(rstanarm)

@@

```{r, echo=FALSE, include=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(rstanarm)
library(ggplot2)
library(loo)

@@

# Create the model comparison table using gt
model_comparison <- tibble(
  Model = c("model_date", "model_date_pollster", "model_date_pollster_national"),
  AIC = c(AIC(model_date), AIC(model_date_pollster), AIC(model_date_pollster_national)),
  BIC = c(BIC(model_date), BIC(model_date_pollster), BIC(model_date_pollster_national))
)

@@

# Load necessary libraries
library(gt)
library(loo)

>>>>

library(tidyverse)
library(gt)
library(ggplot2)
library(tidyr)
library(arrow)
library(here)
library(rstanarm)
library(broom)
library(loo)
data = read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
# Read the Parquet file
analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))

@@

We use the polling data to forecast the potential outcomes of the 2024 U.S. presidential election between Kamala Harris and Donald Trump.The dataset was obtained from https://projects.fivethirtyeight.com/polls/president-general/2024/national/ or (FiveThirtyEight’s “Poll of Polls” for the 2024 U.S. Presidential election [@fivethirtyeight2024]). It provides a comprehensive view of voter preferences through aggregated results from numerous national polls conducted by various polling organizations. The dataset was simulated, cleaned, analyzed, and tested using the R programming language [@talia], tidyverse [@citetidyverse], knitr [@citeknitr], ggplot2 [@citeggplot2] for plots, gt[@gt] for tables, tidyr[@R-tidyr], arrow[@R-arrow] for parquet, here[@R-here], rstanarm[@R-rstanarm], broom[@R-broom], loo[@R-loo], lubridate [@R-lubridate], while tibble [@R-tibble] helped simplify data frame management. The testthat package [@R-testthat] was essential for unit testing and ensuring code reliability, and we employed styler [@R-styler] for reformatting and maintaining a consistent code style.

@@

```{r}
#| label: fig-reliability
#| fig-cap: "Average Support Percentage by Pollster Reliability"
#| echo: false

@@

@@

```{r}
#| label: fig-samplesize
#| fig-cap: "Candidate Vote Percentages by Sample Size Category"
#| echo: false
# Categorizing sample size into small, medium, and large groups

@@

```{r}
#| label: fig-sponsorship
#| fig-cap: "Vote Percentages by Partisan Sponsorship"
#| echo: false
# Calculate the average pct and standard deviation for each candidate by sponsorship type
sponsorship_summary_data <- data %>%
  filter(sponsor_candidate_party != "Non-Partisan") %>%  # Focus on partisan-sponsored polls
  group_by(candidate_name, sponsor_candidate_party) %>%
  summarise(
    avg_pct = mean(pct),
    sd_pct = sd(pct),
    .groups = 'drop'
  )

@@

@@

```{r, echo=FALSE, include=FALSE, warning=FALSE}

@@

# Create the model comparison table using gt
model_comparison <- tibble(
  Model = c("model_date", "model_date_pollster", "model_date_pollster_national"),
  AIC = c(AIC(model_date), AIC(model_date_pollster), AIC(model_date_pollster_national)),
  BIC = c(BIC(model_date), BIC(model_date_pollster), BIC(model_date_pollster_national)),
)

@@

# Load necessary libraries
